\section{Machine learning methods for wind turbine condition monitoring}

% \begin{table*}
%     \centering
%     \ra{1.3}
%     \caption{Summary of machine learning methods for wind turbine condition monitoring}
%     \begin{tabular}{lp{2.5cm}p{5cm}p{6cm}}
%         \toprule
%         Nr & Input & Feature extraction method & Machine learning model \\
%         \midrule
%         \cite{ml_cm_wt_blade_ARMA_2018} & Vibration signal. & ARMA model and J48 decision tree & Tests a set of (38) meta-, misc-, rule- and tree-based classifiers for FD in blades. \\ 
%         \cite{AD_and_fault_analysis_wt_DAE} & SCADA data. & & Deep auto-encoder made of RBMs to model normal behaviour of SCADA variables. Uses reconstruction error for AD. \\
%         \cite{unsup_graphical_modeling_wt_cm} & SCADA data. & Spatiotemporal pattern network & Unsupervised use of RBMs for AD. \\
%         \cite{fault_detection_and_isolation_using_classifier_fusion} & SCADA data. & Time-frequency domain analysis, DWT and ARMA model & Uses fusion of MLP, RBF, decision tree, KNN, SVM for FD of wind turbine.  \\
%         \cite{lin_and_non_lin_feat_for_ice_detection_on_blades} & Ultrasonic testing. & Tests linear and non-linear PCA and ARMA models & Neighbourhood component analysis for feature selection. Tests 20 different supervised classifiers for detecting ice on blades. \\
%         \cite{perf_mon_of_wt_using_extreme_func_theory} & Wind-Power curve. &  & Uses Gaussian Process regression with extreme fucntion theory to determine whether a particular power curve is an outlier.\\
%         \cite{blade_damage_detection_sup_ml_alg} & Acustic emission. & FFT. & Uses Distinguishability Measure for feature selection, and logistic regression and SVM for binary blade fault classification. \\
%         \cite{wt_cm_using_cloud_computing_and_HELM} & Power signal, wind speed and ambient temperature signals. & & Hierarchical Extreme Learning Machine\\
%         \cite{GP_operational_curve_monitoring} & SCADA data. & & Gaussian processes regression to estimate wind-power curve \\
%         \cite{high_freq_scada_perf_monit_sensitivity} & SCADA data. & Tests KNN, random forest, and SVR to estimate power curve. Detects anomalies by reconstruction error.& \\
%         \cite{dict_learning_monitor_wt_drivetrain_bearing} & Vibration signals. & & Uses unsupervised dictionary learning extracting features which are then used to determine fault in drivetrain bearings. \\
%         \cite{ANN_damage_detection_gearbox_wt} & Oil temperature, wind speed and rotor speed. & & Trains ANN to estimate vibration signal, uses reconstruction error for AD. \\
%         \cite{multiway_PCA_multivar_inference_cm_wt} & SCADA data. & PCA. & Sets up baseline model using multiway PCA, then finds outliers by hypothesis testing whether multivariate distribution is equal to baseline. \\
%         \cite{image_texture_analysis_FD_wt} & FAST wind turbine simulator. & Image texture analysis tools. & KNN, Linear Discriminant Model, decision trees, bag-tree, linear SVM.\\
%         \cite{auto_associative_nn_wt_fault_detection} & SCADA data. & K-means for outlier elimination. & Uses Auto-Associative Neural Networks as an auto-encoder, and the Hotel T2 statistic as a dynamic threshold for the reconstruction error.\\
%         \cite{abnormal_detection_scada_data_mining} & SCADA data. & Grey correlation algorithm for eigencevtor extraction. & Use genetic algorithm for feature selection, and SVR for estimating performance curves. \\
%         \cite{health_cond_model_nn_proportional_hazard_models} & Rotor speed, gearbox temperature and generator temperature. & & Uses three NN for normal behaviour modelling. Reconstruction error sendt to proportional hazard model which sets dynamic threshold. \\
%         \cite{ice_detection_using_ITL} & SCADA data. & & Uses Inductive Transfer Learning and five differen ML classifiers for ice detection on blades. \\
%         \cite{VMD_MPE_COVAL_fault_detection_gearbox} & Vibration signals. & Variational mode decomposition (VMD). & Uses multi-scale permutation entropy (MPE) used for feature selection, COVAL for domain normalization and an SVM for binary fault classification.\\
%         \cite{SVR_blade_pitch_curve_cm} & SCADA data. & & Uses bins and SVR to estimate blade angle pitch curve. \\
%         \cite{detecting_malfunctions_wt_generator_bearings_generic_vs_specific_models} & SCADA data. &  & Tests different architectures of ANNs to for estimating temperature of non-drive end bearing. Uses reconstruction error for anomaly detection. \\
%         \cite{image_based_surface_damage_detection_DL_drone_inspection} & Images taken by drones & & Recurrent Convolutional Neural Network to classify structural damage in blades.\\
%         \cite{image_based_YOLO_YSODA} & Uses images taken from ground level & & Convolutional Neural Network, and YOLO-based small object detection approach (YSODA) for damage detection in blades and hub.\\
%         \cite{vibration_acustic_decision_tree_SVM_gearbox} & Vibration signals, acustic signals and oil particle analysis & DWT. & Uses decision tree for feature selection, and SVC for assessing fault severity in gearbox\\
%         \cite{AI_image_analytics_2_classify_blade_defects} & Uses images taken from ground level & & Convolutional Neural Network to detect cracks $\&$ damage in blades.\\
%         \cite{dirt_n_mud_detection_using_guided_waves} & Ultrasonic testing & PCA and ARMA models. & Neighbourhood Component analysis for feature selection and an ensamble of KNN, linear SVM, decision trees, LDA and subspace discriminant to estimate amount of dirt and mud on blades. \\
%         \cite{fault_classification_using_CSO_SVM} & & & \\
%         % \cite{} & & & \\
%         % \cite{} & & & \\
%         \bottomrule
%     \end{tabular}
% \end{table*}

\begin{longtable}{p{0.03\textwidth}p{0.2\textwidth}p{0.3\textwidth}p{0.4\textwidth}}
    \hline
    Nr & Input & Feature extraction method & Machine learning model \\
    \hline \hline
    \cite{ml_cm_wt_blade_ARMA_2018} & Vibration signal. & ARMA model and J48 decision tree & Tests a set of (38) meta-, misc-, rule- and tree-based classifiers for FD in blades. \\  \hline
    \cite{AD_and_fault_analysis_wt_DAE} & SCADA data. & & Deep auto-encoder made of RBMs to model normal behaviour of SCADA variables. Uses reconstruction error for AD. \\ \hline
    \cite{unsup_graphical_modeling_wt_cm} & SCADA data. & Spatiotemporal pattern network & Unsupervised use of RBMs for AD. \\ \hline
    \cite{fault_detection_and_isolation_using_classifier_fusion} & SCADA data. & Time-frequency domain analysis, DWT and ARMA model & Uses fusion of MLP, RBF, decision tree, KNN, SVM for FD of wind turbine.  \\ \hline
    \cite{lin_and_non_lin_feat_for_ice_detection_on_blades} & Ultrasonic testing. & Tests linear and non-linear PCA and ARMA models & Neighbourhood component analysis for feature selection. Tests 20 different supervised classifiers for detecting ice on blades. \\ \hline
    \cite{perf_mon_of_wt_using_extreme_func_theory} & Wind-Power curve. &  & Uses Gaussian Process regression with extreme fucntion theory to determine whether a particular power curve is an outlier.\\ \hline
    \cite{blade_damage_detection_sup_ml_alg} & Acustic emission. & FFT. & Uses Distinguishability Measure for feature selection, and logistic regression and SVM for binary blade fault classification. \\ \hline
    \cite{wt_cm_using_cloud_computing_and_HELM} & Power signal, wind speed and ambient temperature signals. & & Hierarchical Extreme Learning Machine\\ \hline
    \cite{GP_operational_curve_monitoring} & SCADA data. & & Gaussian processes regression to estimate wind-power curve \\ \hline
    \cite{high_freq_scada_perf_monit_sensitivity} & SCADA data. & Tests KNN, random forest, and SVR to estimate power curve. Detects anomalies by reconstruction error.& \\ \hline
    \cite{dict_learning_monitor_wt_drivetrain_bearing} & Vibration signals. & & Uses unsupervised dictionary learning extracting features which are then used to determine fault in drivetrain bearings. \\ \hline
    \cite{ANN_damage_detection_gearbox_wt} & Oil temperature, wind speed and rotor speed. & & Trains ANN to estimate vibration signal, uses reconstruction error for AD. \\ \hline
    \cite{multiway_PCA_multivar_inference_cm_wt} & SCADA data. & PCA. & Sets up baseline model using multiway PCA, then finds outliers by hypothesis testing whether multivariate distribution is equal to baseline. \\ \hline
    \cite{image_texture_analysis_FD_wt} & FAST wind turbine simulator. & Image texture analysis tools. & KNN, Linear Discriminant Model, decision trees, bag-tree, linear SVM.\\ \hline
    \cite{auto_associative_nn_wt_fault_detection} & SCADA data. & K-means for outlier elimination. & Uses Auto-Associative Neural Networks as an auto-encoder, and the Hotel T2 statistic as a dynamic threshold for the reconstruction error.\\ \hline
    \cite{abnormal_detection_scada_data_mining} & SCADA data. & Grey correlation algorithm for eigencevtor extraction. & Use genetic algorithm for feature selection, and SVR for estimating performance curves. \\ \hline
    \cite{health_cond_model_nn_proportional_hazard_models} & Rotor speed, gearbox temperature and generator temperature. & & Uses three NN for normal behaviour modelling. Reconstruction error sendt to proportional hazard model which sets dynamic threshold. \\ \hline
    \cite{ice_detection_using_ITL} & SCADA data. & & Uses Inductive Transfer Learning and five differen ML classifiers for ice detection on blades. \\ \hline
    \cite{VMD_MPE_COVAL_fault_detection_gearbox} & Vibration signals. & Variational mode decomposition (VMD). & Uses multi-scale permutation entropy (MPE) used for feature selection, COVAL for domain normalization and an SVM for binary fault classification.\\ \hline
    \cite{SVR_blade_pitch_curve_cm} & SCADA data. & & Uses bins and SVR to estimate blade angle pitch curve. \\ \hline
    \cite{detecting_malfunctions_wt_generator_bearings_generic_vs_specific_models} & SCADA data. &  & Tests different architectures of ANNs to for estimating temperature of non-drive end bearing. Uses reconstruction error for anomaly detection. \\ \hline
    \cite{image_based_surface_damage_detection_DL_drone_inspection} & Images taken by drones & & Recurrent Convolutional Neural Network to classify structural damage in blades.\\ \hline
    \cite{image_based_YOLO_YSODA} & Uses images taken from ground level & & Convolutional Neural Network, and YOLO-based small object detection approach (YSODA) for damage detection in blades and hub.\\ \hline
    \cite{vibration_acustic_decision_tree_SVM_gearbox} & Vibration signals, acustic emission and oil particle analysis & DWT. & Uses decision tree for feature selection, and SVC for assessing fault severity in gearbox\\ \hline
    \cite{AI_image_analytics_2_classify_blade_defects} & Uses images taken from ground level & & Convolutional Neural Network to detect cracks $\&$ damage in blades.\\ \hline
    \cite{dirt_n_mud_detection_using_guided_waves} & Ultrasonic testing & PCA and ARMA models. & Neighbourhood Component analysis for feature selection and an ensamble of KNN, linear SVM, decision trees, LDA and subspace discriminant to estimate amount of dirt and mud on blades. \\ \hline
    \cite{fault_classification_using_CSO_SVM} & Uses pitch position, rotor speed and generator speed. & & Detects faults with an SVC with parameters optimized by Cuckoo-swarm optimization. \\ \hline
    \cite{vibration_ARMA_decision_tree_cm_wt} & Vibration signals & ARMA model. & Dominating features selected with J48 decision tree, fault classification done with Bayesian- and lazy classifiers. \\ \hline
    \cite{integrated_cm_bearing_fault_wt_gearbox} & Vibration signals, acustic emission and oil particle analysis & DWT and PCA. & Dominating features selected with decision tree, fault detection done with SVC. \\ \hline
    \cite{blade_defect_detection_imaging_array} & Images taken from imaging array & & Uses a deep neural network for binary classification of blade defects. \\ \hline
    \cite{unsupervised_AD_blade_damage_deep_features_images} & Uses images taken by drone & Uses a CNN trained on an unrelated image dataset to extract general features. & Compress features with PCA, and pass them to a unsupervised one-class SVM. \\ \hline
    \cite{vibration_fault_diagnosis_wt_planetary_gearbox} & & & This is a literary review of vibration based condition monitoring and fault diagnosis of planetary gearboxes in wind turbines. \\ \hline
    \cite{RF_XGB_fault_detection} & Uses the FAST wind turbine simulator to get SCADA data. & Random forest. & Uses XGBoost to train an ensamble of classifiers for specific faults. \\ \hline
    \cite{CBPM_ABPM_maintainance_model} & SCADA data. & & Uses several ANN to build a normal behaviour model, then uses reconstruction error together with the age of the age of the turbine to predict anomolous behaviour.\\ \hline
    \cite{improved_power_curve_monitoring_of_wt} & SCADA data. & & Uses Pearson product-moment rank correlation to select features, and applies different ANN structures to predict the active power. \\ \hline
    \cite{DBN_simulink_SCADA_FD} & SCADA data from a simulink model of a wind turbine. & & Uses Deep Belief Networks for detecting anomolous behaviour.\\ \hline
    \cite{wt_gearbox_bearing_temp_KS_CNN} & SCADA data. &  & Uses kolmogorov-smirnov test to compare different turbines at same moment in time combined with the reconstruction error of the gearbox bearing temperature of an ANN to detect anomalies.\\ \hline
    \cite{fault_monitoring_HMM} & Vibration signals. & Approximates vibration distributions at different rotor speeds with Weibull distribution. & Uses a HMM for statistical fault detection. \\ \hline
    \cite{model_based_fuzzy_logic_cm_wt} & SCADA data. & & Compares linear models, ANNs and state-dependent parameter models for fault detection. \\ \hline
    \cite{fault_detect_PARAFAC_k_means} & SCADA data. & parallel factor analysis (PARAFAC) as a decomposition method & uses K-means clustering after decomposition for fault detection. \\ \hline
    \cite{online_fd_using_PCA_different_operating_zones} & Uses a wind turbine simulator for SCADA data. & & Multiple PCA models are as a statistical reference reflecting the data variability in local zones and used in parallel for online fault detection. \\ \hline
    \cite{roller_bearings_cm_fisher_score_and_permutation_entropy} & Vibration signals. & Variational mode decomposition & Uses Fisher score and ReliefF algorithm for feature selection. Feeds selected signals into a multi-class SVC for bearing fault detection. \\ \hline
    \cite{deep_learning_for_imbalanced_class_detection_bearing_cm} & SCADA data. & & Uses deep neural networks for detection of icing on the blades. \\ \hline
    \cite{perform_monitoring_wt_using_ASI_methods} & Wind speed, ambient temperature and air density. & & Uses a series of ARMA models (ARIMA, GAS, GASX, NLGASX) to predict the potential for energy production at a geographical location. \\ \hline
    \cite{reliability_analysis_detecting_FA_NN_wt} & SCADA data. & & Combines NN with alarms generated by SCADA system to reduce false alarm rate. \\ \hline
    \hline
    \caption{Summary of machine learning methods for wind turbine condition monitoring}
    \label{tab:machine_learning_wt_cm_summary}
\end{longtable}